Network Slicing and Resource Allocation in an Open RAN System \vspace{-.1cm}

### 2021-06-15 Latex/journal_v1/V4/pr.tex
add algorithm

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of O-RU and Fronthaul Capacity}
Let $P_r$ denote the power of transmitted signal from the $r^{th}$ O-RU to UEs served by it.
From \eqref{eq2}, we have,
\begin{equation}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q_{r(s,j)}}^2.
\end{equation}
Since we have fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}
C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q_{r}}^2})},
\end{equation}
Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q_{r}}^2$ is the power of quantization noise.
\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Also, the transmission delay is the amount of time required to push all the packets into the fiber link. 
($T = \frac{\alpha}{R}$ Where, $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of the each link which is constant in this model.)
Here we assume the value of propagation delay and transmission is negligible compared to the rest.
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.

@@

In addition, $T_{RU}^{s}$ is the mean transmission delay of $s^{th}$ slice on the wireless link. The arrival data rate of wireless link is equal to the arrival data rate of load balancers for each service.
 %\cite{frdl}.
Moreover, it is assumed that the service time of transmission queue for each slice $s$ has
 an exponential distribution with mean $1/(R_{{tot}_s})$ and can be modeled as a M/M/1 queue.
 %\cite{frdl,luong2018novel,luong2018novel1,guo2016exploiting}. 
 Therefore,
the mean delay of the transmission layer is
\begin{equation}
 T_{RU}^{s} = \frac{1}{R_{{tot}_s} - \alpha_{s}};
\end{equation}
where, $R_{{tot}_s} = \sum_{u=1}^{U_s}a_{u(s,i)}R_{u(s,i)}$ is the total achievable rate of each service.
So the mean processing delay for each UE in slice $s$ is 
\begin{equation}
T_{process}^{s} =  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s}
\end{equation}

@@

&T_{tot}^s \leq T_{tot}^{max,s} \quad \forall s,\label{c16} \\

@@

where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}] \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i \forall r, \forall k$ indicate the binary variable for PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i \forall r$ is a binary variable for O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.

@@

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
To convexify \eqref{eq11} (for the short packet transmission), we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}. So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{equation}
\begin{split}
\hat{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\hat{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\hat{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}\\
\end{split}
\end{equation}
Consider UPF, O-CU and O-DU have the same processor (for simplification), so we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. 
As a result of these assumption, for simplicity, we can assume that $M_s = M_s^u = M_s^c = M_s^d $
Using the above assumption, we have $T_{DU}^{s} = T_{CU}^{s} = T_{UPF}^{s}$ 
\begin{equation}
\begin{split}
T_{process}^{s} &=  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s} \\
T_{process}^{s} &=  T_{RU}^{s} + 3\times T_{DU}^{s}.
\end{split}
\end{equation}
\begin{lemma}
In problem \eqref{problem}, if we change the constraint \eqref{c16} to equality, the optimality of the  
system will not be changed \cite{SystemCostMinimization}
\end{lemma}

>>>>

If we replace $p_{u(s,l)}^{k}$ and $p_{u(n,l)}^{k}$ in \eqref{eqI} by $P_{max}$, an upper bound $\bar{I}_{r,u(s,i)}^{k}$ is obtained for $I_{r,u(s,i)}^{k}$. Therefore, $\bar{\mathcal{R}}_{u_{(s,i)}} \forall s , \forall i$ is derived by using $\bar{I}_{r,u(s,i)}^{k}$ instead of $I_{r,u(s,i)}^{k}$ in  \eqref{eq11} and \eqref{eq3}.
\subsection{Power of O-RU and Fronthaul Capacity}
Let $P_r$ denote the power of transmitted signal from the $r^{th}$ O-RU to UEs served by it.
From \eqref{eq2}, we have,
\begin{equation}
P_r = \sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}+ \sigma_{q_{r(s,j)}}^2.
\end{equation}
Since we have fiber link between O-RU and O-DU, the rate of users on the fronthual link between O-DU and the $r^{th}$ O-RU  is formulated as
%\cite{simeone2016cloud, 1111}
\begin{equation}
C_{r} = \log{(1+ \frac{\sum_{s=1}^{S}\sum_{k=1}^{K_s}\sum_{i=1}^{U_s}|\bold{w}_{r,u(s,i)}^{k}|^2 \mathcal{\alpha}^k_{r,u(s,i)} }{ \sigma_{q_{r}}^2})},
\end{equation}
Where, $\mathcal{\alpha}^k_{r,u(s,i)}= p_{r,u(s,i)}^{k} g_{u(s,i)}^r e^k_{r,u(s,i)}$ and $\sigma_{q_{r}}^2$ is the power of quantization noise.
\subsection{Mean Delay}
In this part, the end to end mean delay for a service is obtained.
Suppose the mean total delay is depicted as $T_{tot}$.
\begin{equation}
\begin{split}
T_{tot} &=  T_{process} + T_{transmission} + T_{propagation}\\
T_{process} &=  T_{RU} + T_{DU} + T_{CU} + T_{UPF}\\
T_{transmission} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
T_{propagation} &= T_{front} + T_{mid} + T_{back} + T_{trans2net} \\
\end{split}
\end{equation}
%T_{tot} = T_{RU} + T_{front} + T_{DU} + T_{mid} + T_{CU} + T_{back} + T_{core} + T_{trans2net}
Total delay is sum of processing delay, transmission delay and propagation delay. 
The propagation delay is the time takes for a signal to reach to its destination. So it has a constant value based on the length of fiber link ($T = L/c$, where $L$ is the length of link and c is the speed of signal).
Also, the transmission delay is the amount of time required to push all the packets into the fiber link. 
($T = \frac{\alpha}{R}$ Where, $R$ is the rate of transmission in each link and $\alpha$ is the mean arrival data rate of the each link which is constant in this model.)
Here we assume the value of propagation delay and transmission is negligible compared to the rest.
\begin{equation}
T_{tot} \approx T_{process}
\end{equation}
\subsubsection{Processing Delay}
Assume the packet arrival of UEs follows a Poisson process with arrival rate $\lambda_{u(s,i)}$ for the $i^{th}$ UE of the $s^{th}$ slice.
Therefore, the mean arrival data rate of the $s^{th}$ slice in the UPF layer is $\alpha_{s}^1 = \sum_{u=1}^{U_s}a_{u(s,i)}\lambda_{u(s,i)}$, where $a_{u(s,i)}$ is a binary variable which indicates whether the $i^{th}$ UE requested $s^{th}$ service is admitted or not.

@@

In addition, $T_{RU}^{u(s,i)}$ is the mean transmission delay of $i^{th}$ UE in $s^{th}$ service on the wireless link.
 The arrival data rate of wireless link for each UE i in service s is $\lambda_{u(s,i)}$
As a result we have, $\sum_{i = 1}^{U_s} \lambda_{u(s,i)} = \alpha_s$.
Moreover, The service time of transmission queue for UE $i$ requesting service $s$ has
an exponential distribution with mean $1/(R_{u(s,i)}$ and can be modeled as a M/M/1 queue.

Therefore, the mean delay of the transmission layer for UE $i$ in slice $s$ is
\begin{equation}
 T_{RU}^{u(s,i)} = \frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}};
\end{equation}

So the mean processing delay for each UE $i$ in slice $s$ is 
T_{process}^{u(s,i)} =  T_{RU}^{u(s,i)} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s}
Hence, $T_{tot}^{u(s,i)} \approx T_{process}^{u(s,i)} $

@@

&T_{tot}^{u(s,i)}  \leq T_{max}^{s} \quad \forall i,\forall s,\label{c16} \\
& \mu_s \geq \alpha_s/M_s \quad \forall s,\label{c16-1} \\
& \mathcal{R}_{u_{(s,i)}} \geq {\lambda}_{u_{(s,i)}} \quad \forall i,\forall s,\label{c16-2} \\
& 0 \leq M_s \leq M^{max}  \quad \forall s,\label{c16-3}\\

@@

where $\boldsymbol{P} =[p_{r,u(s,i)}^{k}] \:\: \forall s , \forall i, \forall r, \forall k $, is the matrix of power for UEs, $\boldsymbol{E} =[e_{r,u(s,i)}^k] \:\: \forall s , \forall i, \forall r, \forall k$ indicate the binary variable for PRB association. Moreover, $\boldsymbol{G} =[g_{u(s,i)}^r] \:\: \forall s , \forall i, \forall r$ is a binary variable for O-RU association. Furthermore, $M = [M_s^d, M_s^c, M_s^u] \:\: \forall s$ is the matrix that shown the number of VNFs in each layer of slice.

@@

\eqref{c16-1} and \eqref{c16-2} denoted the stability of the M/M/1 queue model.
\eqref{c16-3} restricted the number of VNF in each slice due to the limited resources.

@@

Suppose $\hat{\rho}_{r,u(s,i)}^{k} =  \frac{|P_{max}{\bold{h}_{r,u(s,i)}^{H \: k}} \bold{w}_{r,u(s,i)}^{k} g_{u(s,i)}^r|^2}{BN_0}$. 
To convexify \eqref{eq11} (for the short packet transmission), we replace ${\rho}_{r,u(s,i)}^{k}$ with $\hat{\rho}_{r,u(s,i)}^{k}$ in \eqref{shortPacket}. So, a lower bound for \eqref{eq11} is given that is a concave function.
\begin{split}
\hat{\mathcal{R}}_{u(s_j,i)}^{r} &= \sum_{k=1}^{K_{s_j}} B (\log_2({1+ \rho_{u(s_2,i)}^{k}})- \hat{\zeta}_{u(s_j,i)}^{k}){e}_{u(s_j,i)}^{k}\\
\hat{\mathcal{R}}_{u(s_j,i)} &= \sum_{r=1}^{R}\hat{\mathcal{R}}_{u(s_j,i)}^{r}\\ 
 \hat{\zeta}_{u(s_j,i)}^{k} =& log_2({e})Q^{-1}(\epsilon) \sqrt{\frac{\hat{\mathfrak{C}}_{u(s_j,i)}^{k}}{N_{u(s_j,i)}^{k}}})\\
 \hat{\mathfrak{C}}_{u(s_j,i)}^{k} =& 1 - \frac{1}{(1+\hat{\rho}_{u(s_j,i)}^{k})^2}\\
\end{split}
Consider UPF, O-CU and O-DU have the same processor (for simplification), so we have $\mu_s = \mu_s^u \approx \mu_s^c \approx \mu_s^d $. Moreover, as mentioned before,
the mean arrival data rate of the UPF layer for a service $s$ ($\alpha_{s}^U$) is approximately equal to the mean arrival data rate of the O-CU-UP layer ($\alpha_{s}^C$) and O-DU ($\alpha_{s}^D$). so $\alpha_{s} =\alpha_{s}^U \approx \alpha_{s}^C \approx \alpha_{s}^D$. 
As a result of these assumption, for simplicity, we can assume that $M_s = M_s^u = M_s^c = M_s^d $
Using the above assumption, we have $T_{DU}^{s} = T_{CU}^{s} = T_{UPF}^{s}$ 
\begin{split}
T_{process}^{s} &=  T_{RU}^{s} + T_{DU}^{s} + T_{CU}^{s} + T_{UPF}^{s} \\
T_{process}^{s} &=  T_{RU}^{s} + 3\times T_{DU}^{s}.
\end{split}
\begin{lemma}
In problem \eqref{problem}, the constraint \eqref{c16} can be reformulated as below
$ \forall i,\forall s$
\begin{split}
&T_{max}^s \geq\frac{1}{R_{u(s,i)} - \lambda_{u(s,i)}} + \frac{3}{\mu_s - \alpha_{s}/{M_s}}  \\
&M_s \geq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }\\
\end{split}
Also from equation \eqref{c19}, \eqref{c16-1} and \eqref{c16-3} we have
0\leq M_s \leq \min\{M^{max}, \alpha_s/\mu_s, \phi_{max}/{3\phi_s}\}
We denote $ \mathfrak{M}_s= \min\{M^{max}, \alpha_s/\mu_s, \phi_{max}/{3\phi_s}\}$.
Thus, if we restrict \eqref{c16} to equality we have
\begin{equation}\label{eqDelay}
0\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
In \eqref{eqDelay}, $0\leq \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$ is established due to the fact that 
the numerator and the denominator will be both negative. Using \eqref{c16-2},
in numerator, $\alpha_s \geq 0$, $ R_{u(s,i)}-\lambda_{u(s,i)} \geq 0$ and 
$(R_{u(s,i)}-\lambda_{u(s,i)})T_{max}^s \leq 1$. So the numerator is negative.
In denominator, it can be said approximately that $(T_{max}^s\mu_s)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s \leq 0 $, since, $(R_{u(s,i)}-\lambda_{u(s,i)}) \leq 1/T_{max}^s$.
Therefore, we just need to have constraint below
\begin{equation}\label{constraint16}
\frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s } \leq \mathfrak{M}_s
So by reformulating the equation \eqref{constraint16}, we have a new constraint $\forall i, \forall s$ as below,
R_{u(s,i)} \geq \frac{\mathfrak{M}_s ((T_{max}^s\mu_s-3)\lambda_{u(s,i)} + \mu_s) - \alpha_s(T_{max}^s\lambda_{u(s,i)} +1) }{\mathfrak{M}_s (T_{max}^s\mu_s-3)-\alpha_s T_{max}^s}.
In addition, we denote $\mathtt{M}_{u(s,i)} = \frac{\alpha_s(T_{max}^s R_{u(s,i)}-T_{max}^s\lambda_{u(s,i)} -1)}{(T_{max}^s\mu_s-3)(R_{u(s,i)}-\lambda_{u(s,i)}) - \mu_s }$.
So we have,
M_s = \max\{\mathtt{M}_{u(s,i)} | i \in 1,2,..., U_s\} \quad \forall s .
\end{lemma}
Despite simplifying the problem \eqref{problem}, it is still non-convex and hard to be solved.
So the simplest approach is to relax $\mathbf{E}$ into continuous value $e_{r,u(s,i)}^k \in [0,1] \:\: \forall s , \forall i ,\forall r, \forall k$
Furthermore, the problem can  be solved using the Lagrangian function and iterative algorithm.
In order to make \eqref{constraints1} as a standard form of a convex optimization problem, it is required to change the variable of equations \eqref{cc14} and \eqref{cc15} ($p_{r_{(s,i)}} = \sigma_{q_{r(s,j)}}^2\times 2^{C_{r_{(s,i)}}}$ and $1/(D_{s}- d_{s_1} + d_{s_2})+\alpha_s$ respectively).
Assume $\boldsymbol{\lambda}$, $\boldsymbol{\mu}$, $\boldsymbol{\xi}$, and $\boldsymbol{ \kappa}$ are the matrix of Lagrangian multipliers that have non-zero positive elements.
The Lagrangian function is written as follow
\begin{subequations}\label{lagrang}
\mathcal{L}(\boldsymbol{P}; \boldsymbol{\lambda}, \boldsymbol{\chi}, \boldsymbol{\mu}, \boldsymbol{ \xi}, \boldsymbol{ \kappa}) & = \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v}\mathcal{\bar{R}}_{u_{(v,k)}}
- \eta \sum\limits_{v=1}^{V} \sum\limits_{i=1}^{\mathcal{R}_s}\bar{p}_{r_{(s,i)}}\\
&+\sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \lambda_{u_{(v,k)}} (\mathcal{\bar{R}}_{u_{(v,k)}}-\mathcal{R}_{u_{(v,k)}}^{max})\\
&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \mu_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-P_{max})\\
&- \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} \xi_{r_{(s,i)}} (\bar{p}_{r_{(s,i)}}-\sigma_{q_{r(s,i)}}^2 2^{C_{r_{(s,i)}}^{max}}).\\
&+ \sum\limits_{v=1}^{V} \sum\limits_{k=1}^{U_v} \kappa_{u_{(v,k)}} \sum\limits_{s=1}^{S}(R_{u_{(v,k)}} -\mathfrak{D_s})a_{v,s}.
where, $\mathfrak{D_s}=\frac{1}{D_{s}^{max}-d_{s_1}-d_{s_2}}+\alpha_s$. Optimal power is obtained from  \eqref{lagrang}
p_{u(v,i)}^{*} = [\frac{\mathfrak{y}_{u(v,i)}\mathfrak{w}_{u(v,i)}-\mathfrak{x}_{u(v,i)}\mathfrak{z}_{u(v,i)}}{\mathfrak{x}_{u(v,i)}\mathfrak{w}_{u(v,i)} }]^+
where, $\mathfrak{y}_{u(v,i)}= (\lambda_{u(v,i)}+\kappa_{u_{(v,k)}}+1)\frac{B}{Ln_2}$ and
$\mathfrak{w}_{u(v,i)} = \sum_{s=1}^{S}|\bold{h}_{R_s,u(v,i)}^H \bold{w}_{R_s,u(v,i)}|^2 a_{v,s}$. Also
$\mathfrak{z}_{u(v,i)} = BN_0 + \bar{I}_{u(v,i)}$ and $\mathfrak{x}_{u(v,i)} = \sum\limits_{s=1}^{S} \sum\limits_{i=1}^{R_s} ( \mu_{r_{u(s,i)}} + \xi_{r_{(s,i)}}+\eta)||w_{r_{(s,j)},u_{(v,i)}}||^2$.
By using sub-gradient method, the optimal power $\boldsymbol{P}$ is obtained \cite{mimoCran}.
